\myfont Implementation and evaluation of register allocation for translating LLVM-{}- to x86-64

### 2024-01-14 article.tex
Add phis final

@@

\subsubsection{\lstinline!benches/phis.ll!}
Coalescing with the Briggs allocator is evidently quite beneficial, as the it does out perform most benchmarks. This is obviously because eliminating movs stand to gain. A more direct approach to demonstrating this is with parameterized benchmarks. While in theory a phi node has the potential to eliminate one \texttt{mov} instruction, in practice this might be more beneficial due to the implementation.
The \texttt{benches/phis.py <n> <m>} script will generate a \texttt{.ll} program consisting of \(m\) phi nodes over \(n\) iterations.
%Parameterized over how many phi moves need to be made per iteration. Sure most time might be spent in \texttt{@printf}, but this is constant across all runs, and in fact serves a purpose of adding extra load.
 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 33699586& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49352x& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49358x& \cellcolor[rgb]{0.8115234375,0.9990234375,0.75} 1.24889x& \cellcolor[rgb]{0.8115234375,0.9990234375,0.75} 1.24890x& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49352x& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49355x& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49351x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 11.61953x\\
 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 33696431& \cellcolor[rgb]{0.9990234375,0.9814453125,0.75} 2.54359x& \cellcolor[rgb]{0.9990234375,0.9814453125,0.75} 2.55986x& \cellcolor[rgb]{0.8740234375,0.9990234375,0.75} 1.49846x& \cellcolor[rgb]{0.873046875,0.9990234375,0.75} 1.49796x& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49373x& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49378x& \cellcolor[rgb]{0.9990234375,0.9814453125,0.75} 2.54356x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 11.52326x\\
 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 50475128& \cellcolor[rgb]{0.9453125,0.9990234375,0.75} 1.78694x& \cellcolor[rgb]{0.998046875,0.9990234375,0.75} 1.99722x& \cellcolor[rgb]{0.791015625,0.9990234375,0.75} 1.16621x& \cellcolor[rgb]{0.83203125,0.9990234375,0.75} 1.33250x& \cellcolor[rgb]{0.9150390625,0.9990234375,0.75} 1.66480x& \cellcolor[rgb]{0.9150390625,0.9990234375,0.75} 1.66483x& \cellcolor[rgb]{0.94140625,0.9990234375,0.75} 1.77143x& \cellcolor[rgb]{0.9990234375,0.7939453125,0.75} 8.57567x\\
 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 67274018& \cellcolor[rgb]{0.935546875,0.9990234375,0.75} 1.74795x& \cellcolor[rgb]{0.966796875,0.9990234375,0.75} 1.87263x& \cellcolor[rgb]{0.76171875,0.9990234375,0.75} 1.04956x& \cellcolor[rgb]{0.7646484375,0.9990234375,0.75} 1.06208x& \cellcolor[rgb]{0.8740234375,0.9990234375,0.75} 1.49853x& \cellcolor[rgb]{0.8115234375,0.9990234375,0.75} 1.24908x& \cellcolor[rgb]{0.87890625,0.9990234375,0.75} 1.52063x& \cellcolor[rgb]{0.9990234375,0.8564453125,0.75} 6.57981x\\
 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 84029983& \cellcolor[rgb]{0.8486328125,0.9990234375,0.75} 1.39938x& \cellcolor[rgb]{0.9482421875,0.9990234375,0.75} 1.79869x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00002x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00003x& \cellcolor[rgb]{0.82421875,0.9990234375,0.75} 1.29955x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00004x& \cellcolor[rgb]{0.9990234375,0.8681640625,0.75} 6.19846x& \cellcolor[rgb]{0.9990234375,0.875,0.75} 5.98194x\\
 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 100810530& \cellcolor[rgb]{0.8740234375,0.9990234375,0.75} 1.49925x& \cellcolor[rgb]{0.95703125,0.9990234375,0.75} 1.83217x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99997x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99996x& \cellcolor[rgb]{0.8115234375,0.9990234375,0.75} 1.24967x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99998x& \cellcolor[rgb]{0.9990234375,0.9169921875,0.75} 4.60493x& \cellcolor[rgb]{0.9990234375,0.8798828125,0.75} 5.80149x\\
 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 117587019& \cellcolor[rgb]{0.837890625,0.9990234375,0.75} 1.35669x& \cellcolor[rgb]{0.9462890625,0.9990234375,0.75} 1.78907x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.88585x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.90488x& \cellcolor[rgb]{0.802734375,0.9990234375,0.75} 1.21403x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.85730x& \cellcolor[rgb]{0.9990234375,0.9326171875,0.75} 4.10513x& \cellcolor[rgb]{0.9990234375,0.888671875,0.75} 5.51438x\\
 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 134365885& \cellcolor[rgb]{0.8740234375,0.9990234375,0.75} 1.49947x& \cellcolor[rgb]{0.9521484375,0.9990234375,0.75} 1.81229x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.87512x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.87515x& \cellcolor[rgb]{0.7958984375,0.9990234375,0.75} 1.18732x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.87514x& \cellcolor[rgb]{0.9990234375,0.947265625,0.75} 3.63380x& \cellcolor[rgb]{0.9990234375,0.9111328125,0.75} 4.81382x\\
\end{NiceTabular}

1074877208

@@

phis & clang & simple 12 & simple 2 & briggs 12 & briggs 2 & linear 2 & linear 12 & greedy 12 & greedy 0 \\
 0 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 150762& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99922x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00386x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00104x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99880x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00325x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99096x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00077x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99764x\\
 1 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 263112& \cellcolor[rgb]{0.9453125,0.9990234375,0.75} 1.78765x& \cellcolor[rgb]{0.9580078125,0.9990234375,0.75} 1.83810x& \cellcolor[rgb]{0.8154296875,0.9990234375,0.75} 1.26448x& \cellcolor[rgb]{0.9365234375,0.9990234375,0.75} 1.75223x& \cellcolor[rgb]{0.9384765625,0.9990234375,0.75} 1.75782x& \cellcolor[rgb]{0.939453125,0.9990234375,0.75} 1.76278x& \cellcolor[rgb]{0.9453125,0.9990234375,0.75} 1.78716x& \cellcolor[rgb]{0.9990234375,0.865234375,0.75} 6.27904x\\
 2 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 333724& \cellcolor[rgb]{0.8603515625,0.9990234375,0.75} 1.44531x& \cellcolor[rgb]{0.8955078125,0.9990234375,0.75} 1.58670x& \cellcolor[rgb]{0.7734375,0.9990234375,0.75} 1.09621x& \cellcolor[rgb]{0.7978515625,0.9990234375,0.75} 1.19483x& \cellcolor[rgb]{0.8466796875,0.9990234375,0.75} 1.39069x& \cellcolor[rgb]{0.8466796875,0.9990234375,0.75} 1.39096x& \cellcolor[rgb]{0.8642578125,0.9990234375,0.75} 1.45969x& \cellcolor[rgb]{0.9990234375,0.896484375,0.75} 5.28416x\\
 3 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 399042& \cellcolor[rgb]{0.8720703125,0.9990234375,0.75} 1.49027x& \cellcolor[rgb]{0.892578125,0.9990234375,0.75} 1.57311x& \cellcolor[rgb]{0.7568359375,0.9990234375,0.75} 1.03136x& \cellcolor[rgb]{0.7587890625,0.9990234375,0.75} 1.03867x& \cellcolor[rgb]{0.8310546875,0.9990234375,0.75} 1.32618x& \cellcolor[rgb]{0.7900390625,0.9990234375,0.75} 1.16354x& \cellcolor[rgb]{0.8310546875,0.9990234375,0.75} 1.32695x& \cellcolor[rgb]{0.9990234375,0.9169921875,0.75} 4.61992x\\
 4 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 464640& \cellcolor[rgb]{0.8193359375,0.9990234375,0.75} 1.28048x& \cellcolor[rgb]{0.8896484375,0.9990234375,0.75} 1.56253x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00015x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99836x& \cellcolor[rgb]{0.8017578125,0.9990234375,0.75} 1.21081x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99861x& \cellcolor[rgb]{0.9990234375,0.9375,0.75} 3.96512x& \cellcolor[rgb]{0.9990234375,0.9208984375,0.75} 4.48737x\\
 5 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 529535& \cellcolor[rgb]{0.841796875,0.9990234375,0.75} 1.37214x& \cellcolor[rgb]{0.9033203125,0.9990234375,0.75} 1.61569x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99931x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99959x& \cellcolor[rgb]{0.7939453125,0.9990234375,0.75} 1.17952x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99948x& \cellcolor[rgb]{0.9990234375,0.94921875,0.75} 3.58774x& \cellcolor[rgb]{0.9990234375,0.921875,0.75} 4.47259x\\
 6 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 594553& \cellcolor[rgb]{0.818359375,0.9990234375,0.75} 1.27726x& \cellcolor[rgb]{0.9013671875,0.9990234375,0.75} 1.61016x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.91261x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.92786x& \cellcolor[rgb]{0.7900390625,0.9990234375,0.75} 1.16424x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.89141x& \cellcolor[rgb]{0.9990234375,0.955078125,0.75} 3.38554x& \cellcolor[rgb]{0.9990234375,0.921875,0.75} 4.46924x\\
 7 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 659461& \cellcolor[rgb]{0.8486328125,0.9990234375,0.75} 1.39945x& \cellcolor[rgb]{0.90234375,0.9990234375,0.75} 1.61499x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.90111x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.90219x& \cellcolor[rgb]{0.787109375,0.9990234375,0.75} 1.15128x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.90144x& \cellcolor[rgb]{0.9990234375,0.96484375,0.75} 3.08855x& \cellcolor[rgb]{0.9990234375,0.935546875,0.75} 4.03288x\\

@@

phis & clang & simple 12 & simple 2 & briggs 12 & briggs 2 & linear 2 & linear 12 & greedy 12 & greedy 0 \\
 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 150756& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00269x& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00742x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00356x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00237x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99991x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00269x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99794x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00298x\\

>>>>

phis & clang & simple 12 & simple 2 & briggs 12 & briggs 2 & linear 12 & linear 2 & greedy 12 & greedy 0 \\
 0 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1073928603& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49981x& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49981x& \cellcolor[rgb]{0.8115234375,0.9990234375,0.75} 1.24997x& \cellcolor[rgb]{0.8115234375,0.9990234375,0.75} 1.24997x& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49981x& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49982x& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49981x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 11.68360x\\
 1 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1073928952& \cellcolor[rgb]{0.9990234375,0.9814453125,0.75} 2.54982x& \cellcolor[rgb]{0.9990234375,0.9794921875,0.75} 2.60344x& \cellcolor[rgb]{0.8740234375,0.9990234375,0.75} 1.49994x& \cellcolor[rgb]{0.8740234375,0.9990234375,0.75} 1.49994x& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49981x& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49983x& \cellcolor[rgb]{0.9990234375,0.9814453125,0.75} 2.54981x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 11.58368x\\
 2 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 1610830251& \cellcolor[rgb]{0.9384765625,0.9990234375,0.75} 1.75897x& \cellcolor[rgb]{0.998046875,0.9990234375,0.75} 1.99991x& \cellcolor[rgb]{0.791015625,0.9990234375,0.75} 1.16665x& \cellcolor[rgb]{0.83203125,0.9990234375,0.75} 1.33330x& \cellcolor[rgb]{0.9150390625,0.9990234375,0.75} 1.66660x& \cellcolor[rgb]{0.9150390625,0.9990234375,0.75} 1.66663x& \cellcolor[rgb]{0.9375,0.9990234375,0.75} 1.75644x& \cellcolor[rgb]{0.9990234375,0.798828125,0.75} 8.40916x\\
 3 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 2147723548& \cellcolor[rgb]{0.9365234375,0.9990234375,0.75} 1.74997x& \cellcolor[rgb]{0.9677734375,0.9990234375,0.75} 1.87495x& \cellcolor[rgb]{0.76171875,0.9990234375,0.75} 1.05002x& \cellcolor[rgb]{0.7646484375,0.9990234375,0.75} 1.06250x& \cellcolor[rgb]{0.8115234375,0.9990234375,0.75} 1.24999x& \cellcolor[rgb]{0.8740234375,0.9990234375,0.75} 1.49997x& \cellcolor[rgb]{0.8828125,0.9990234375,0.75} 1.53576x& \cellcolor[rgb]{0.9990234375,0.853515625,0.75} 6.64460x\\
 4 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 2684621503& \cellcolor[rgb]{0.849609375,0.9990234375,0.75} 1.40001x& \cellcolor[rgb]{0.9482421875,0.9990234375,0.75} 1.79998x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.82421875,0.9990234375,0.75} 1.29999x& \cellcolor[rgb]{0.9990234375,0.8916015625,0.75} 5.43928x& \cellcolor[rgb]{0.9990234375,0.8740234375,0.75} 5.99128x\\
 5 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 3221532192& \cellcolor[rgb]{0.8740234375,0.9990234375,0.75} 1.49997x& \cellcolor[rgb]{0.95703125,0.9990234375,0.75} 1.83329x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00000x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99999x& \cellcolor[rgb]{0.8115234375,0.9990234375,0.75} 1.24999x& \cellcolor[rgb]{0.9990234375,0.9169921875,0.75} 4.60720x& \cellcolor[rgb]{0.9990234375,0.8798828125,0.75} 5.82084x\\
 6 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 3758430778& \cellcolor[rgb]{0.8388671875,0.9990234375,0.75} 1.35714x& \cellcolor[rgb]{0.9462890625,0.9990234375,0.75} 1.78839x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.88572x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.90478x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.85715x& \cellcolor[rgb]{0.802734375,0.9990234375,0.75} 1.21428x& \cellcolor[rgb]{0.9990234375,0.9326171875,0.75} 4.10980x& \cellcolor[rgb]{0.9990234375,0.8876953125,0.75} 5.54983x\\
 7 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 4295303796& \cellcolor[rgb]{0.8740234375,0.9990234375,0.75} 1.50000x& \cellcolor[rgb]{0.9521484375,0.9990234375,0.75} 1.81439x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.87500x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.87502x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.87500x& \cellcolor[rgb]{0.7958984375,0.9990234375,0.75} 1.18750x& \cellcolor[rgb]{0.9990234375,0.9482421875,0.75} 3.62761x& \cellcolor[rgb]{0.9990234375,0.91015625,0.75} 4.84205x\\
\caption{\label{tab:phis}Benchmark of \texttt{benches/phis\{0..7\}.ll} output by \mintinline{bash}{dune exec bench -- -f phis -n 16}}

@@

%\subsubsection{\lstinline!benches/phis.ll!}
%Coalescing with the Briggs allocator is evidently quite beneficial, as the it does out perform most benchmarks. This is obviously because eliminating movs stand to gain. A more direct approach to demonstrating this is with parameterized benchmarks. While in theory a phi node has the potential to eliminate one \texttt{mov} instruction, in practice this might be more beneficial due to the implementation.
%The \texttt{benches/phis.py <n> <m>} script will generate a \texttt{.ll} program consisting of \(m\) phi nodes over \(n\) iterations.
%Parameterized over how many phi moves need to be made per iteration. Sure most time might be spent in \texttt{@printf}, but this is constant across all runs, and in fact serves a purpose of adding extra load.

%\begin{NiceTabular}{|c|ccccccccc|}
%\hline
%arg(s) & clang & simple 12 & simple 2 & briggs 12 & briggs 2 & linear 2 & linear 12 & greedy 12 & greedy 0 \\
%\hline
 %& \cellcolor[rgb]{0.75,0.9990234375,0.75} 33699586& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49352x& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49358x& \cellcolor[rgb]{0.8115234375,0.9990234375,0.75} 1.24889x& \cellcolor[rgb]{0.8115234375,0.9990234375,0.75} 1.24890x& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49352x& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49355x& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49351x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 11.61953x\\
 %& \cellcolor[rgb]{0.75,0.9990234375,0.75} 33696431& \cellcolor[rgb]{0.9990234375,0.9814453125,0.75} 2.54359x& \cellcolor[rgb]{0.9990234375,0.9814453125,0.75} 2.55986x& \cellcolor[rgb]{0.8740234375,0.9990234375,0.75} 1.49846x& \cellcolor[rgb]{0.873046875,0.9990234375,0.75} 1.49796x& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49373x& \cellcolor[rgb]{0.9990234375,0.9833984375,0.75} 2.49378x& \cellcolor[rgb]{0.9990234375,0.9814453125,0.75} 2.54356x& \cellcolor[rgb]{0.9990234375,0.75,0.75} 11.52326x\\
 %& \cellcolor[rgb]{0.75,0.9990234375,0.75} 50475128& \cellcolor[rgb]{0.9453125,0.9990234375,0.75} 1.78694x& \cellcolor[rgb]{0.998046875,0.9990234375,0.75} 1.99722x& \cellcolor[rgb]{0.791015625,0.9990234375,0.75} 1.16621x& \cellcolor[rgb]{0.83203125,0.9990234375,0.75} 1.33250x& \cellcolor[rgb]{0.9150390625,0.9990234375,0.75} 1.66480x& \cellcolor[rgb]{0.9150390625,0.9990234375,0.75} 1.66483x& \cellcolor[rgb]{0.94140625,0.9990234375,0.75} 1.77143x& \cellcolor[rgb]{0.9990234375,0.7939453125,0.75} 8.57567x\\
 %& \cellcolor[rgb]{0.75,0.9990234375,0.75} 67274018& \cellcolor[rgb]{0.935546875,0.9990234375,0.75} 1.74795x& \cellcolor[rgb]{0.966796875,0.9990234375,0.75} 1.87263x& \cellcolor[rgb]{0.76171875,0.9990234375,0.75} 1.04956x& \cellcolor[rgb]{0.7646484375,0.9990234375,0.75} 1.06208x& \cellcolor[rgb]{0.8740234375,0.9990234375,0.75} 1.49853x& \cellcolor[rgb]{0.8115234375,0.9990234375,0.75} 1.24908x& \cellcolor[rgb]{0.87890625,0.9990234375,0.75} 1.52063x& \cellcolor[rgb]{0.9990234375,0.8564453125,0.75} 6.57981x\\
 %& \cellcolor[rgb]{0.75,0.9990234375,0.75} 84029983& \cellcolor[rgb]{0.8486328125,0.9990234375,0.75} 1.39938x& \cellcolor[rgb]{0.9482421875,0.9990234375,0.75} 1.79869x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00002x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00003x& \cellcolor[rgb]{0.82421875,0.9990234375,0.75} 1.29955x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00004x& \cellcolor[rgb]{0.9990234375,0.8681640625,0.75} 6.19846x& \cellcolor[rgb]{0.9990234375,0.875,0.75} 5.98194x\\
 %& \cellcolor[rgb]{0.75,0.9990234375,0.75} 100810530& \cellcolor[rgb]{0.8740234375,0.9990234375,0.75} 1.49925x& \cellcolor[rgb]{0.95703125,0.9990234375,0.75} 1.83217x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99997x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99996x& \cellcolor[rgb]{0.8115234375,0.9990234375,0.75} 1.24967x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99998x& \cellcolor[rgb]{0.9990234375,0.9169921875,0.75} 4.60493x& \cellcolor[rgb]{0.9990234375,0.8798828125,0.75} 5.80149x\\
 %& \cellcolor[rgb]{0.75,0.9990234375,0.75} 117587019& \cellcolor[rgb]{0.837890625,0.9990234375,0.75} 1.35669x& \cellcolor[rgb]{0.9462890625,0.9990234375,0.75} 1.78907x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.88585x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.90488x& \cellcolor[rgb]{0.802734375,0.9990234375,0.75} 1.21403x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.85730x& \cellcolor[rgb]{0.9990234375,0.9326171875,0.75} 4.10513x& \cellcolor[rgb]{0.9990234375,0.888671875,0.75} 5.51438x\\
 %& \cellcolor[rgb]{0.75,0.9990234375,0.75} 134365885& \cellcolor[rgb]{0.8740234375,0.9990234375,0.75} 1.49947x& \cellcolor[rgb]{0.9521484375,0.9990234375,0.75} 1.81229x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.87512x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.87515x& \cellcolor[rgb]{0.7958984375,0.9990234375,0.75} 1.18732x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.87514x& \cellcolor[rgb]{0.9990234375,0.947265625,0.75} 3.63380x& \cellcolor[rgb]{0.9990234375,0.9111328125,0.75} 4.81382x\\
%\hline
%\end{NiceTabular}

%1074877208

@@

%\begin{table}[H]
%\makebox[\textwidth][c]{
%\begin{NiceTabular}{|c|ccccccccc|}
%\hline
%phis & clang & simple 12 & simple 2 & briggs 12 & briggs 2 & linear 2 & linear 12 & greedy 12 & greedy 0 \\
%\hline
 %0 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 150762& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99922x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00386x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00104x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99880x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00325x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99096x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00077x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99764x\\
 %1 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 263112& \cellcolor[rgb]{0.9453125,0.9990234375,0.75} 1.78765x& \cellcolor[rgb]{0.9580078125,0.9990234375,0.75} 1.83810x& \cellcolor[rgb]{0.8154296875,0.9990234375,0.75} 1.26448x& \cellcolor[rgb]{0.9365234375,0.9990234375,0.75} 1.75223x& \cellcolor[rgb]{0.9384765625,0.9990234375,0.75} 1.75782x& \cellcolor[rgb]{0.939453125,0.9990234375,0.75} 1.76278x& \cellcolor[rgb]{0.9453125,0.9990234375,0.75} 1.78716x& \cellcolor[rgb]{0.9990234375,0.865234375,0.75} 6.27904x\\
 %2 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 333724& \cellcolor[rgb]{0.8603515625,0.9990234375,0.75} 1.44531x& \cellcolor[rgb]{0.8955078125,0.9990234375,0.75} 1.58670x& \cellcolor[rgb]{0.7734375,0.9990234375,0.75} 1.09621x& \cellcolor[rgb]{0.7978515625,0.9990234375,0.75} 1.19483x& \cellcolor[rgb]{0.8466796875,0.9990234375,0.75} 1.39069x& \cellcolor[rgb]{0.8466796875,0.9990234375,0.75} 1.39096x& \cellcolor[rgb]{0.8642578125,0.9990234375,0.75} 1.45969x& \cellcolor[rgb]{0.9990234375,0.896484375,0.75} 5.28416x\\
 %3 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 399042& \cellcolor[rgb]{0.8720703125,0.9990234375,0.75} 1.49027x& \cellcolor[rgb]{0.892578125,0.9990234375,0.75} 1.57311x& \cellcolor[rgb]{0.7568359375,0.9990234375,0.75} 1.03136x& \cellcolor[rgb]{0.7587890625,0.9990234375,0.75} 1.03867x& \cellcolor[rgb]{0.8310546875,0.9990234375,0.75} 1.32618x& \cellcolor[rgb]{0.7900390625,0.9990234375,0.75} 1.16354x& \cellcolor[rgb]{0.8310546875,0.9990234375,0.75} 1.32695x& \cellcolor[rgb]{0.9990234375,0.9169921875,0.75} 4.61992x\\
 %4 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 464640& \cellcolor[rgb]{0.8193359375,0.9990234375,0.75} 1.28048x& \cellcolor[rgb]{0.8896484375,0.9990234375,0.75} 1.56253x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00015x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99836x& \cellcolor[rgb]{0.8017578125,0.9990234375,0.75} 1.21081x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99861x& \cellcolor[rgb]{0.9990234375,0.9375,0.75} 3.96512x& \cellcolor[rgb]{0.9990234375,0.9208984375,0.75} 4.48737x\\
 %5 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 529535& \cellcolor[rgb]{0.841796875,0.9990234375,0.75} 1.37214x& \cellcolor[rgb]{0.9033203125,0.9990234375,0.75} 1.61569x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99931x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99959x& \cellcolor[rgb]{0.7939453125,0.9990234375,0.75} 1.17952x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99948x& \cellcolor[rgb]{0.9990234375,0.94921875,0.75} 3.58774x& \cellcolor[rgb]{0.9990234375,0.921875,0.75} 4.47259x\\
 %6 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 594553& \cellcolor[rgb]{0.818359375,0.9990234375,0.75} 1.27726x& \cellcolor[rgb]{0.9013671875,0.9990234375,0.75} 1.61016x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.91261x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.92786x& \cellcolor[rgb]{0.7900390625,0.9990234375,0.75} 1.16424x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.89141x& \cellcolor[rgb]{0.9990234375,0.955078125,0.75} 3.38554x& \cellcolor[rgb]{0.9990234375,0.921875,0.75} 4.46924x\\
 %7 & \cellcolor[rgb]{0.75,0.9990234375,0.75} 659461& \cellcolor[rgb]{0.8486328125,0.9990234375,0.75} 1.39945x& \cellcolor[rgb]{0.90234375,0.9990234375,0.75} 1.61499x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.90111x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.90219x& \cellcolor[rgb]{0.787109375,0.9990234375,0.75} 1.15128x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.90144x& \cellcolor[rgb]{0.9990234375,0.96484375,0.75} 3.08855x& \cellcolor[rgb]{0.9990234375,0.935546875,0.75} 4.03288x\\
%\end{NiceTabular}}
%\caption{\label{tab:dumb-fib-greedy}Benchmark of \texttt{benches/fib.ll} output by \mintinline{bash}{dune exec bench -- -f fib -n 1000}}
%\end{table}
%

@@

%\begin{table}[H]
%\makebox[\textwidth][c]{
%\begin{NiceTabular}{|c|ccccccccc|}
%\hline
%phis & clang & simple 12 & simple 2 & briggs 12 & briggs 2 & linear 2 & linear 12 & greedy 12 & greedy 0 \\
%\hline
 %& \cellcolor[rgb]{0.75,0.9990234375,0.75} 150756& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00269x& \cellcolor[rgb]{0.7509765625,0.9990234375,0.75} 1.00742x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00356x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00237x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99991x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00269x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 0.99794x& \cellcolor[rgb]{0.75,0.9990234375,0.75} 1.00298x\\
